Online Multiclass Linear Classification with Bandit Feedback

### 2019-01-09 arxiv-version/related-work.tex

>>>>

The online bandit multiclass learning is a special case of the contextual bandits
problem~\cite{Auer-2003, Langford-Zhang-2008}, where the cost is the classification error.
A series of works in the contextual bandits learning literature focuses on
oracle-efficiency, that is, they assume access to an
oracle that given a set of cost-sensitve learning examples,
